\pkg{evtree}: Evolutionary Learning of Globally Optimal Classification and Regression Trees in \proglang{R}

### 2011-11-11 pkg/evtree/inst/doc/evtree.Rnw
another one
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@270 255f4249-2263-4417-b1ea-8498779e27a7

\textit{Crossover} exchanges, randomly selected, subtrees between two trees. Let
${\theta}_{i}^1$ and ${\theta}_{i}^2$ be the two trees
chosen from the population for crossover. First, two internal nodes $r_1$ and $r_2$
are selected randomly from ${\theta}_{i}^1$ and ${\theta}_{i}^2$, respectively.
Let $\mathrm{sub}1({\theta}_i^j, r_j)$ denote the subtree of $\theta_j$ rooted
by $r_j$ ($j=1,2$), i.e., the tree containing $r_j$ and its descendant nodes.
Then, the complementary part of ${\theta}_{i}^j$ can be defined as 
$\mathrm{sub}2({\theta}_{i}^j, r_j) = {\theta}_{i}^j \setminus \mathrm{sub}1({\theta}_{i}^j, r_j)$. 
The crossover operator creates two new trees
${\theta}_{i+1}^1 = \mathrm{sub}2({\theta}_{i}^1, r_1) \cup \mathrm{sub}1({\theta}_{i}^2, r_2)$ and
${\theta}_{i+1}^2 = \mathrm{sub}2({\theta}_{i}^2, r_2) \cup \mathrm{sub}1({\theta}_{i}^1, r_1)$.
If the crossover creates some invalid nods in either one of the new trees ${\theta}_{i+1}^1$
or ${\theta}_{i+1}^2$, these are omitted.

>>>>

\textit{Crossover} exchanges, randomly selected, subtrees between two trees. Let
${\theta}_{i}^1$ and ${\theta}_{i}^2$ be the two trees
chosen from the population for crossover. First, two internal nodes $r_1$ and $r_2$
are selected randomly from ${\theta}_{i}^1$ and ${\theta}_{i}^2$, respectively.
Let $\mathrm{sub}1({\theta}_i^j, r_j)$ denote the subtree of $\theta_i^j$ rooted
by $r_j$ ($j=1,2$), i.e., the tree containing $r_j$ and its descendant nodes.
Then, the complementary part of ${\theta}_{i}^j$ can be defined as 
$\mathrm{sub}2({\theta}_{i}^j, r_j) = {\theta}_{i}^j \setminus \mathrm{sub}1({\theta}_{i}^j, r_j)$. 
The crossover operator creates two new trees
${\theta}_{i+1}^1 = \mathrm{sub}2({\theta}_{i}^1, r_1) \cup \mathrm{sub}1({\theta}_{i}^2, r_2)$ and
${\theta}_{i+1}^2 = \mathrm{sub}2({\theta}_{i}^2, r_2) \cup \mathrm{sub}1({\theta}_{i}^1, r_1)$.
If the crossover creates some invalid nods in either one of the new trees ${\theta}_{i+1}^1$
or ${\theta}_{i+1}^2$, these are omitted.
